Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

\subsection{Testing}
We tested our algorithms against each other using a mean average precision 
score for each method.  The mean average precision (MAP) algorithm came directly from the Kaggle MSD challenge \citep{kaggleMSD}. The score was used to rank the competition entries.

The MAP scores were computed by calculating the precision between a list of recommendations for a user and that user's test set. The MAP score is then the average precision value over all the users in the test set.

We used two different baseline benchmarks to compare our MAP scores against. THe first was to simply recommend the top 500 most popular songs to every user. This naive method resulted in a MAP score of 0.0138 (top 500 songs based on number of users who listened to the song) or 0.0126 (top 500 songs based on number of plays the song had). The second method was to first recommend a user the most popular songs of artists the user already had played (but different songs from that artist). If this did not result in enough recommendations, we would then recommend the overall most popular songs as well at the end(similar to baseline method 1). Although this method is conservative in that it does not go beyond the tastes the user has already listened to, it resulted in a significant improvement in the MAP score to 0.045.

>>>>

\subsection{Testing}
We tested our algorithms against each other using a mean average precision 
score for each method.  The mean average precision (MAP) calculation came directly from the Kaggle MSD challenge \citep{kaggleMSD}. The score was used to rank the competition entries.

The MAP@500 scores were computed by calculating the precision between a list of recommendations for a user and that user's test set. Specifically, we calculate the average precision at each element in the list of recommended items (i.e. percentage of correct items among first k recommendations) and sum these up for the first 500 recommendations.
We then averaged the score over all users. Intuitively, the score looks at the percentage of recommendations that were correct (i.e. in the test set) but also takes order into account. So it is preferable to recommend the songs in the user's test set earlier in the list of 500.

We used two different baseline benchmarks to compare our MAP scores against. The first was to simply recommend the top 500 most popular songs to every user. This naive method resulted in a MAP score of 0.0138 (top 500 songs based on number of users who listened to the song) or 0.0126 (top 500 songs based on number of plays the song had). The second method was to first recommend a user the most popular songs of artists the user already had played (but different songs from that artist). If this did not result in enough recommendations, we would then recommend the overall most popular songs as well at the end(similar to baseline method 1). Although this method is conservative in that it does not go beyond the tastes the user has already listened to, it resulted in a significant improvement in the MAP score to 0.045.
